\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Fix new typo
from 6505b122ffef1fe5e5020267175a83c2e7e87f6c

We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
We recruited five participants per experimental condition to gather qualitative data; this has been suggested as the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
We recruited twenty users per experimental condition to gather quantitative data, based on estimates of the number needed for statistically significance~\cite{howmanyusers}.

>>>>

We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
We recruited five participants per experimental condition to gather qualitative data; this has been suggested as the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
We recruited twenty users per experimental condition to gather quantitative data, based on estimates of the number needed for statistical significance~\cite{howmanyusers}.
